Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-02-28 rebuttal/rebuttal_response_max_500_words.txt

[Reviewer 2] reason for not reporting Kraken performance on downstream NER
We chose not to report Kraken performances as it would have drastically reduced the size of the labelled sets "NER-x" and thus hampered the other evaluations on the reference, pero and tesseract datasets.
All labelled datasets contains the same subset of directories entries by construction (section 3). Kraken performs quite poorly, which hinders the projection of labels from the ground truth and drastically reduces the size of the subset of labelled entries.

[Reviewer 2] missing Figure 1 reference, inconsistent reference to figures, Tesseract spelling
Thanks for pointing these issues, [TODO] we fixed them.
(Refs. to figures fixed)
(About T/tesseract : is he refering to fig 7 ? If so, "tesseract" is the name of the test set from "NER-tesseract").

[Reviewer 2] Experiment with artificial OCR noise in future work
We plan to perform such experiments following e.g. the techniques presented in https://doi.org/10.1007/978-3-030-86331-9_48
As it seems to be quite hard to generate realistic noise, we decided to first focus on real cases with no further assumptions.

[Reviewer 3] Section 2.3 should be a separate section about the pipeline
We extracted this content as a new section as suggested.
We have also moved the subsection "Metrics for OCR and NER Quality assessment" from the former section 3 "Dataset" to this new section.

### 2022-02-28 src-latex/parts/00-abstract.tex
WIP rebuttal
Ref to fig. 1 + mention to thumbnails

% !TeX root = ../main-paper.tex
This paper features a comparison of four (\bertrand{Ensure it's 4!} named entity recognition (NER) techniques which can be reasonably used in the context of historical document analysis.
Such natural language processing techniques identify which class each text token belong to, like "person name", "location", "number" or "activity".
Introducing a new public dataset built from 19th century French directories, 
we perform a practical assessment of the accuracy of, and the annotation cost (considering various training set sizes) needed by each technique.
We also study the impact of real OCR noise for several OCR systems on the performance of NER.
Experiments suggest that FIXME APPROACH NAME is the most effective approach on the dataset we processed.
FIXME add numerical results
Results can be reproduced using data and code freely available at \url{https://github.com/soduco/paper-ner-bench-das22}
and the latest version of is paper can be obtained at \url{TODO arxiv URL}.

>>>>

% !TeX root = ../main-paper.tex
Named entity recognition (NER) is a necessary step in many pipelines targeting historical documents.
Indeed, such natural language processing techniques identify which class each text token belongs to,
e.g. ``person name'', ``location'', ``number''.
Introducing a new public dataset built from 19th century French directories,
we first assess how noisy modern, off-the-shelf OCR are.
Then, we compare modern CNN- and Transformer-based NER techniques
which can be reasonably used in the context of historical document analysis.
We measure their requirements in terms of training data,
the effects of OCR noise on their performance,
and show how Transformer-based NER can benefit from unsupervised pre-training 
and supervised fine-tuning on noisy data (\cref{fig.pipeline-overview}).
Results can be reproduced using resources available at \url{https://github.com/soduco/paper-ner-bench-das22}.
% The latest version of is paper can be obtained at \url{https://arxiv.org/abs/xxxx.xxxxx}.
